Derive final annotations based on NBAtlas reference

### 2025-08-14 analyses/cell-type-neuroblastoma-04/final-annotation.Rmd
path

---
title: "Derive final annotations based on NBAtlas reference"
author: "Stephanie J. Spielman"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  scanvi_pp_threshold: 0.75    
  annotations_tsv: "../results/SCPCP000004-annotations.tsv"
---

>>>>

---
title: "Derive final annotations based on NBAtlas reference"
author: "Stephanie J. Spielman"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  scanvi_pp_threshold: 0.75    
  annotations_tsv: "results/SCPCP000004-annotations.tsv"
---
